%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4in,top=0.3in,right=0.4in,bottom=0.3in]{geometry} % Document margins
\usepackage{tabularx}

\name{ BO WANG } % Your name
\address{ 2021 Ivy Road, Charlottesville, VA 22903 } % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
\address{(434) 249-1640 \\ bw6qh@virginia.edu} % Your phone number and email

\begin{document}
Rich hands-on experience in data management and interpretation and prediction through statistical analysis, machine learning and visualization. Skilled at statistical software and programming language including R, SAS, SQL and Python.


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Virginia, Charlottesville, VA} \hfill {\em May 2017} \\ 
PhD in Mathematics, concentration in Probability \hspace{11mm}  GPA: 3.9/4  \\
%Related Courses: Linear Models, Time Series, Multivariate Statistics, Statistical Consulting, Statistical Computing, Experimental Design,   Categorical Data Analysis, Machine Learning, Bayesian Methods.\\
{\bf Xiamen University, Xiamen, China} \hfill {\em Jun 2012} \\ 
B.S. in Mathematics \hspace{65mm} GPA: 3.9/4\\
%Related Courses: Real Analysis, Numerical Analysis, Graph Theory, Probability. \\
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Prediction on the Churn for Telecom Company }{\em Apr 2015}{}{}
\item Analyzed historical marketing data to predict the propensity of customers churn. Used Logistic Regression and Decision Trees for feature selection and classified the churn status with Random Forests.
\item Performed data cleaning and modeling in Python.


\end{rSubsection}

\begin{rSubsection}{Analysis of Consumer Characters for Automobile Preference  }{ \em Dec 2014}{}{}
\item Investigated the impact of consumer characters by PCA to project national origin preference in mid-sized cars, verified character difference by ANOVA.
\item Built a Bayesian model to identify the dependence of consumer preference across a social network.
\end{rSubsection}

\begin{rSubsection}{Exploration on Factors Causing Flight Delay }{\em Apr 2014}{}{}
\item Recognized patterns in delayed flights through visualizing delay rate on influential factors, such as departure, destination, carrier, travel day and time.
\item Managed a 12 GB data set of commercial flight records through SQL and R interaction.

\end{rSubsection}

\begin{rSubsection}{Discriminant Analysis on Identifying Type II Diabetes }{\em Oct 2013}{}{}
\item Recognized patterns in changing of glucagon and insulin and identified biomarker for disease development from animal experimental data using visualization and T-test.
\item Classified subjects from clinical trial data for human using discriminant analysis.
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}


\begin{rSubsection}{CCB Principal Asset Management}{\em Dec 2015 - Jan 2016}{Quantative Analyst}{Beijing, China}
\item Collaborated with a team to project future sales of oncology drugs in China for Merck Serono, analyzed survival and sales data in Excel.
\item Investigated major competitors of the client based on market size, market share and growth trend.
\item Undertook secondary research on epidemiology and clinical trials, updated deck using Power Point.

\end{rSubsection}


\begin{rSubsection}{The Bank of China (Headquarters)}{\em Jun 2011 - Sep 2011}{Analyst in Custody and Investors Service Department}{Beijing, China}
\item Conducted case studies on family firm succession and published the research on a business magazine.
\item Examined the effect of Family Trust on family firm financial performance using fixed effect model in SAS.  

\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
C++, Matlab, SQL, Python, Bash, Haskel.

\end{rSection}


%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Technical & SAS Certified Advanced Programmer; experienced in R, SQL and Excel;\\
%         & working knowledge of Python and Unix.\\
%Language & Fluent in English, native speaker of Chinese(Mandarin).
%\end{tabular}




%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}



%----------------------------------------------------------------------------------------


\end{document}
