%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4in,top=0.3in,right=0.4in,bottom=0.3in]{geometry} % Document margins
\usepackage{tabularx}

\name{ BO WANG } % Your name
\address{ 2021 Ivy Road, Charlottesville, VA 22903 } % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
\address{(434) 249-1640 \\ bw6qh@virginia.edu} % Your phone number and email

\begin{document}
Rich hands-on experience in analyzing and implementing mathematical models. Skilled at programming language including C++, Matlab, Python, Haskell and SQL. 


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Virginia, Charlottesville, VA} \hfill {\em May 2017} \\ 
PhD in Mathematics, concentration in Probability \hspace{11mm}  GPA: 3.9/4  \\
%Related Courses: Linear Models, Time Series, Multivariate Statistics, Statistical Consulting, Statistical Computing, Experimental Design,   Categorical Data Analysis, Machine Learning, Bayesian Methods.\\
{\bf Xiamen University, Xiamen, China} \hfill {\em Jun 2012} \\ 
B.S. in Mathematics \hspace{65mm} GPA: 3.9/4\\
%Related Courses: Real Analysis, Numerical Analysis, Graph Theory, Probability. \\
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Prediction on the Churn for Telecom Company }{\em Nov 2015}{}{}
\item Analyzed historical marketing data to predict the propensity of customers churn. Used Logistic Regression and Decision Trees for feature selection and classified the churn status with Random Forests.
\item Performed data cleaning and modeling in Python.


\end{rSubsection}

\begin{rSubsection}{Characterization the Volatility using GARCH Model}{ \em Oct 2015}{}{}
\item Set up the GARCH(1,1) model and estimated the parameters by MLE, then predicted the volatility.
\item Implemented the model with Haskell and sped up the calculation using parallelization.
\end{rSubsection}

\begin{rSubsection}{Forecasting the Urban Water Supply}{\em Apr 2015}{}{}
\item Cleaned data and extracted the trend using Matlab Wavelet Toolbox.
\item Implemented the Grey Model GM(1,1) with Matlab to forecast the urban water consumption.
\item Built the BP neural network to find the relation between water comsumption and factors like weather, date and price and gave the optimal price to maximize the profit.

\end{rSubsection}
\begin{rSubsection}{Pricing of the Asian Call Option}{\em Oct 2014}{}{}
\item Analyzed the payoff of the exotic option in the Black-Scholes model.
\item Implemented the pricing using Monte Carlo method with C++.
\end{rSubsection}

\begin{rSubsection}{some c++}{\em Oct 2014}{}{}
\item 
\item 
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}


\begin{rSubsection}{CCB Principal Asset Management}{\em Dec 2015 - Jan 2016}{Quantative Analyst}{Beijing, China}
\item Developed the multi-factor selection system and back-tested the factors.
\item Analyzed the pricing models and searched for the statistical arbitrage signal.
\item Developed the investment models and trading strategies.

\end{rSubsection}




\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
C++, Matlab, SQL, Python, Bash, Haskel.

\end{rSection}



%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Technical & SAS Certified Advanced Programmer; experienced in R, SQL and Excel;\\
%         & working knowledge of Python and Unix.\\
%Language & Fluent in English, native speaker of Chinese(Mandarin).
%\end{tabular}




%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%asdasdasd

%\end{rSection}



%----------------------------------------------------------------------------------------


\end{document}
